Practical Performance Evaluation of Entity Resolution Algorithms: Lessons Learned at PatentsView.org

### 2022-06-27 paper/main.tex
Updates from Overleaf

The specific values for $A_s$, $B_s$, and $T$ in each of our representation is described in appendix X.

@@

\section{Appendix}

@@

This section describes specific values for $A_s$, $B_s$, and $T$ in \eqref{eq:bias_adjustment} in order to obtained nearly unbiased precision and recall estimators based on each of the representation in XX. We use the symbols $\widehat P$ and $\widehat R$, indexed by one of ``$\text{rec}$", ``$\text{clust}$", and ``$\text{block}$", in order to refer to precision and recall estimators corresponding to record, cluster, and block sampling representations.

>>>>

The specific values for $A_s$, $B_s$, and $T$ in each of our representation is described in appendix \ref{sec:appendix}.

@@

\section{Appendix}\label{sec:appendix}

@@

This section describes specific values for $A_s$, $B_s$, and $T$ in \eqref{eq:bias_adjustment} in order to obtained nearly unbiased precision and recall estimators based on each of the representation in section \ref{sec:proposed_estimators}. We use the symbols $\widehat P$ and $\widehat R$, indexed by one of ``$\text{rec}$", ``$\text{clust}$", and ``$\text{block}$", in order to refer to precision and recall estimators corresponding to record, cluster, and block sampling representations.
